Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-01-31 supCLT.tex
supCLT.tex: 1213

%%%----Versions-----------------------------
% supclt1209.tex 2018/12/07 by Zhenyao
% supclt1207.tex 2018/12/07 by Renming
% supCLT1204.tex 2018/12/04 by Zhenyao
% supCLT1130.tex 2018/11/30 by Jianjie
% supCLT1124.tex 2018/11/24 by Zhenyao
% supCLT1115.tex 2018/11/15 by Jianjie
% supCLT9.tex ......... by Zhenyao
% supCLT8.tex ......... by Jianjie
% supCLT7.tex ......... by Zhenyao
% supCLT6.tex ......... by Jianjie
% supCLT5.tex ......... by Zhenyao
% supCLT4.tex ......... by Jianjie
% supCLT3.tex 2018/8/25 by Zhenyao
% supCLT2.tex 2018/8/13 by Jianjie
% supCLT1.tex 2018/7/24 by Zhenyao
% supCLT.tex 2018/6/29 by Jianjie
%---The preamble----------------------
\documentclass[12pt]{amsart}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{amsthm}
\usepackage{stackrel}
\usepackage[backref=section]{hyperref}
\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{mathrsfs}
\usepackage{color}
\usepackage{comment}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
\newcommand{\added}[1]{{\color{blue}#1}}\newcommand{\deleted}[1]{{\color{red}#1}}
%\newcommand{\added}[1]{#1}\newcommand{\deleted}[1]{}

%---Top matter------------------------------
\begin{document}
\title
    [CLT for Super-OU processes]
    {CLT for Super-OU Processes with stable Branching}
\author
    [Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
    {Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
\address
    {Yan-Xia Ren\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
\address
    {Zhenyao Sun\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhenyao.sun@pku.edu.cn}
\address
    {Jianjie Zhao\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhaojianjie@pku.edu.cn}
%\begin{abstract}
%\end{abstract}
%\subjclass[2010]{60J80, 60F05}
%\keywords{}p
%\date{}
%\maketitle
%---Contents-----------------------
\begin{abstract}
    Consider a super-OU process $\{X_t, t\geq 0\}$ with branching mechanism $\psi(z)=-\alpha z +z^{1+\beta}$, where $\alpha >0$ and $\beta\in (0,1)$. For each testing function $f$ of at most polynomial growth,
    denote by $\kappa_f$ the order of $f$ in term of the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$. 
    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes: In the small branching rate case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{+\beta}}$ converges weakly.
    In the critical branching rate case, $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{+\beta}}$ converges weakly.
    In the large branching rate case,  $\alpha\beta> \kappa_f b(1+\beta)$, $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$.
\end{abstract}
\maketitle
\section{Introduction}
\subsection{Model}
    Let $d \in \mathbb N:= \{1,2,\dots\}$ and
    $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator 
\begin{equation}
\label{eq: OU generator}
    Lf(x)
        = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
        \quad  x\in \mathbb R^d,
        f \in C^2(\mathbb{R}^d),
\end{equation}
    where $\sigma>0$ and $b>0$ are constants.
    Denote by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
    Let $\psi$ be the function on $\mathbb R_+:= [0,\infty)$ defined by
\begin{equation}\label{mechanism}
    \psi(z)
    := - \alpha z + z^{1+\beta},
    \quad z \in \mathbb R_+,
\end{equation}
	where $\alpha > 0$ and $\beta \in (0,1) $ are constants.
    Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of all finite Borel measures on $\mathbb{R}^d$.
    For all Borel function $f$ and Borel measure $\mu$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
    Put $\|\mu\|=\langle 1,\mu\rangle$.
    We say an $\mathcal{M}(\mathbb{R}^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb{R}^d$, we have
\begin{equation} \label{super}
    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
    = e^{-\langle V_tf, \mu \rangle},
    \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{equation}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
\begin{equation}\label{eq1}
	V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(\xi_s,V_{t-s}f(\xi_s)\big)~ds\Big]
	= \Pi_x [f(\xi_t)],
    \quad x\in \mathbb R^d, t\geq 0.
\end{equation}

@@

\subsection{OU semigroup}

@@

	Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|,

@@

    Let $X$ be the super OU-process discussed in the first subsection.

@@

    Write $\psi_0(z) := \psi(z) + \alpha z$. Then$\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}$.

@@

\subsection{Main Result}

In this subsection, we will give the main results of this paper. Suppose $\mu\in \mathcal M_c(\mathbb R_d)$ has compact support.
\subsubsection{Large Branching Rate}

For each $p\in \mathbb{N}_+^d$, we define
$$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
  For any $\gamma\in (0, \beta)$, we will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$, thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{thm}\label{Theorem11}
     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(f)b(1+\beta)$, then for any $\gamma\in (0, \beta)$,
     as $t\rightarrow \infty$,
     $$e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle \rightarrow\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).$$

     Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence. 
 \end{thm}
For any $t>0$, let $H_t:=e^{-\alpha t}\|X_t\|$, then $H_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $H_{\infty}:=\lim_{t\rightarrow\infty}H_t$,  $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{rem}
    If $\kappa_f=0$, $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11},  for any $\gamma\in (0, \beta)$, as $t\rightarrow \infty$
     $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
    Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
 \end{rem}

\subsubsection{Critical Branching Rate}
    For $f\in \mathcal{P}$, define
\[
    \tilde{m}[f]
    := \langle(-i\phi)^{1+\beta},\varphi\rangle
\]
    where
\[
    \phi(x)
    =\sum_{|p|=\kappa(f)}\langle f,\phi_p\rangle\phi_p(x).
\]
    Denote by $D$ the extinction event of the super OU-process.
\begin{thm}
\label{Theorem12}
    If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$, then, under $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
\[
    \frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}
    \xrightarrow{d} \eta_1, 
    \quad t\rightarrow \infty,
\]
    where $\eta_1$ is a $(1+\beta)$-stable random variable with
\[
    \mathbb{E} [e^{i\theta \eta_1}]
    =\exp(\tilde{m}[\theta f]), 
    \quad \theta\in \mathbb R.
\]
\end{thm}

\subsubsection{Small Branching Rate}

For $f\in \mathcal{P}$, define
\[
    m[f]
    :=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx
\]
\begin{thm}
\label{Theorem13}
    If $f\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa_f b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
    $$\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_2, \quad t\rightarrow \infty,$$
    where $\eta_2$ is a $(1+\beta)$-stable random variable with 
    $$\mathbb{E} [e^{i\theta \eta_2}]=\exp(m[\theta f]), \quad \theta\in \mathbb R.$$
\end{thm}

@@

	For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, define $(A\times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb R^d$.
    Let $a > 0$, define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
    One of the reason for considering $\gamma$-controllable operators is that they have good algebraic properties:
\begin{lem}
\label{lem: property of controllable operators}
    Let $\mathcal D \subset \mathcal P^*$, $\Lambda$ be an index set, and $(A_\lambda)_{\lambda\in \Lambda}$ be a family of operators from $\mathcal D$ to $ \mathcal P^*$. Assume that $(A_\lambda)_{\lambda\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D$.
\begin{itemize}
\item[(1)]
    Suppose that $(\Lambda, \mathscr F)$ is a measurable space
    and that $(\lambda,x)\mapsto A_\lambda f(x)$ is $\mathscr F \otimes \mathscr B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
    For any probability measure $\mu$ on $(\Lambda, \mathscr F)$, write
\[
    A_\mu f(x):= \int_{\Lambda} A_\lambda f (x)~\mu(d\lambda), \quad f\in \mathcal D, x\in \mathbb R^d.
\]
    Then  $\{A_\mu: \mu \text{ is  a probability measure on } (\Lambda, \mathscr F)\}$ is uniformly $\gamma$-controllable on $\mathcal D$.
\item[(2)]
    Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D_0\subset \mathcal P^*$ to $ \mathcal P^*$.
    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D_0$ for some $\beta \in \mathbb R$ and that, for each $\lambda$, $A_\lambda:\mathcal D \to \mathcal D_0$.
    Then  $(B_\delta A_\lambda)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(\gamma\beta)$-controllable on $\mathcal D$.
\item[(3)]
    Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D$ to $ \mathcal P^*$.
    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D$ for some $\beta \in \mathbb R$.
    Then  $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(\gamma+\beta)$-controllable.
\item[(4)]
    Let $a>0$. Suppose that, for each $\lambda \in \Lambda$, $A_\lambda : \mathcal D \to \mathcal P^+$.
    Then $(A^{\times a}_\lambda)_{\lambda \in \Lambda}$ is uniformly $(a\gamma)$-controllable.
\end{itemize}
\end{lem}
\begin{proof}
    (1). Let $(R,S)$ be the $\gamma$-control-pair of $(A_\lambda)_{\lambda\in\Lambda}$ on $\mathcal{D}$. For all $f \in \mathcal{D}$, $x\in \mathbb R^d$ and  probability measure $\mu$ on $(\Lambda, \mathscr F)$,
\[
   |A_{\mu}f(x)|\leq \int_{\Lambda}|A_{\lambda}f(x)|\mu(d\lambda) \leq \int_{\Lambda}R|f|(x)\mu(d\lambda) \leq R|f|(x).
\]

@@

\begin{proof}
    (1). It follows from \eqref{eq: upper bound for vf}, that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$,
\[
    |U_t g(x)|
    \leq \sup_{0\leq u\leq 1}T_u^\alpha |g| (x).
\]
    Now note that $f\mapsto\sup_{0\leq u\leq 1}T^{\alpha}_u|f|$ is monotone and $1$-scalable.

@@

    (4). From (1), (2), (3) and Lemma \ref{lem: property of controllable operators}.(2), we know that the operators
\[
    f
    \mapsto T^{\alpha}_{t-s}\Psi_0(-U_sf)(x),
    \quad 0\leq s\leq t\leq 1
\]
    is uniformly $(1+\beta)$-controllable.
    Combining this with \eqref{eq:chareq2} and Lemma \ref{lem: property of controllable operators}.(1), we get the desired result.

@@

	In fact, let $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx}. (6).

@@

    According to Corollary \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0,1,...,n\}$ we have

>>>>

%%%----Versions-----------------------------
% supclt1213.tex 2018/12/13 by Renming
% supclt1209.tex 2018/12/07 by Zhenyao
% supclt1207.tex 2018/12/07 by Renming
% supCLT1204.tex 2018/12/04 by Zhenyao
% supCLT1130.tex 2018/11/30 by Jianjie
% supCLT1124.tex 2018/11/24 by Zhenyao
% supCLT1115.tex 2018/11/15 by Jianjie
% supCLT9.tex ......... by Zhenyao
% supCLT8.tex ......... by Jianjie
% supCLT7.tex ......... by Zhenyao
% supCLT6.tex ......... by Jianjie
% supCLT5.tex ......... by Zhenyao
% supCLT4.tex ......... by Jianjie
% supCLT3.tex 2018/8/25 by Zhenyao
% supCLT2.tex 2018/8/13 by Jianjie
% supCLT1.tex 2018/7/24 by Zhenyao
% supCLT.tex 2018/6/29 by Jianjie
%---The preamble----------------------
\documentclass[12pt]{amsart}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{amsthm}
\usepackage{stackrel}
\usepackage[backref=section]{hyperref}
\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{mathrsfs}
\usepackage{color}
\usepackage{comment}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{defi}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
\newcommand{\added}[1]{{\color{blue}#1}}\newcommand{\deleted}[1]{{\color{red}#1}}
%\newcommand{\added}[1]{#1}\newcommand{\deleted}[1]{}

%---Top matter------------------------------
\begin{document}
\title
    [CLT for Super-OU processes]
    {CLT for Super-OU Processes with stable Branching}
\author
    [Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
    {Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
\address
    {Yan-Xia Ren\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
\address
   {Renming Song\\
   Department of Mathematics\\
   University of Illinois\\
   Urbana, IL 61801, USA}
   \email{rsong@illinois.edu}
   \thanks{The research of Renming Song is supported in part by a grant from the Simons Foundation (\# 429343, Renming Song)}
\address
    {Zhenyao Sun\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhenyao.sun@pku.edu.cn}
\address
    {Jianjie Zhao\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhaojianjie@pku.edu.cn}
%\begin{abstract}
%\end{abstract}
%\subjclass[2010]{60J80, 60F05}
%\keywords{}p
%\date{}
%\maketitle
%---Contents-----------------------
\begin{abstract}
    Consider a super-OU process $\{X_t, t\geq 0\}$ with branching mechanism $\psi(z)=-\alpha z +z^{1+\beta}$, where $\alpha >0$ and $\beta\in (0,1)$. For each testing function $f$ of at most polynomial growth,
    denote by $\kappa_f$ the order of $f$ in 
%term of the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$. 
the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$. 
    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes: In the small branching rate case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{+\beta}}$ converges weakly.
    In the critical branching rate case, $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{+\beta}}$ converges weakly.
    In the large branching rate case,  $\alpha\beta> \kappa_f b(1+\beta)$, $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$.
\end{abstract}
\maketitle
\section{Introduction}
%\subsection{Model}
\subsection{Model}\label{ss:1.1}
    Let $d \in \mathbb N:= \{1,2,\dots\}$ and
    $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator 
\label{eq: OU generator}
    Lf(x)
        = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
        \quad  x\in \mathbb R^d,
        f \in C^2(\mathbb{R}^d),
    where $\sigma>0$ and $b>0$ are constants.
    Denote by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
    Let $\psi$ be the function on $\mathbb R_+:= [0,\infty)$ defined by
\begin{equation}\label{mechanism}
    \psi(z)
    := - \alpha z + z^{1+\beta},
    \quad z \in \mathbb R_+,
	where $\alpha > 0$ and $\beta \in (0,1) $ are constants.
    Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of all finite Borel measures on $\mathbb{R}^d$.
    For all Borel function $f$ and Borel measure $\mu$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
    Put $\|\mu\|=\langle 1,\mu\rangle$.
    We say an $\mathcal{M}(\mathbb{R}^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb{R}^d$, we have
\begin{equation} \label{super}
    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
    = e^{-\langle V_tf, \mu \rangle},
    \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
\begin{equation}\label{eq1}
	V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(\xi_s,V_{t-s}f(\xi_s)\big)~ds\Big]
	= \Pi_x [f(\xi_t)],
    \quad x\in \mathbb R^d, t\geq 0.

@@

\subsection{OU Semigroup}

@@

	Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|

@@

    Let $X$ be the super OU-process discussed in Subsection \ref{ss:1.1}.

@@

    Write $\psi_0(z) := \psi(z) + \alpha z$. Then $\psi'_0(z) = \psi'(z) + \alpha=(1+\beta)z^{\beta}$.

@@

\subsection{Main Result}
We will use $\mathcal M_c(\mathbb R_d)$ to denote the space of all
finite Borel measures of compact support on $\mathbb R^d$.
In this subsection, we will give the main results of this paper. 
%Suppose $\mu\in \mathcal M_c(\mathbb R_d)$ has compact support.
\subsubsection{Large branching rate}

For each $p\in \mathbb{N}_+^d$, we define
$$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
  For any $\gamma\in (0, \beta)$, we will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in 
%  $L^{1+\gamma}(\mathbb{P}_{\mu})$, 
$L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $\mu\in \mathcal M_c(\mathbb R_d)$,
  thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{thm}\label{Theorem11}
     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(f)b(1+\beta)$, then for 
%     any $\gamma\in (0, \beta)$,
any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R_d)$,
     as $t\rightarrow \infty$,
     $$e^{-(\alpha-\kappa_fb)t}\langle f, X_t\rangle \rightarrow\sum_{|p|=\kappa_f}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu}).$$

     Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence. 
 \end{thm}
For any $t>0$, let $H_t:=e^{-\alpha t}\|X_t\|$, then $H_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $H_{\infty}:=\lim_{t\rightarrow\infty}H_t$,  $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$, for all $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R_d)$.
 \begin{rem}
%    If $\kappa_f=0$, 
Let $f \in \mathcal{P}$.  If $\kappa_f=0$, 
    $\langle f, \phi_{\kappa_f}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11},  
%    for any $\gamma\in (0, \beta)$, as $t\rightarrow \infty$
for any $\gamma\in (0, \beta)$ and any $\mu\in \mathcal M_c(\mathbb R_d)$, as $t\rightarrow \infty$,
     $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle H_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
    Moreover, if $f$ is twice differentiable and all its second order partial derivatives are in $\mathcal{P}$, then we also have almost sure convergence.
 \end{rem}

\subsubsection{Critical branching rate}
    For $f\in \mathcal{P}$, define
\[
    \tilde{m}[f]
    := \langle(-i\phi)^{1+\beta},\varphi\rangle
\]
    where
\[
    \phi(x)
    =\sum_{|p|=\kappa(f)}\langle f,\phi_p\rangle\phi_p(x).
\]
    Denote by $D$ the extinction event of the super OU-process.
\begin{thm}
\label{Theorem12}
    If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$, 
%    then, under 
   then for any $\mu\in \mathcal M_c(\mathbb R_d)$, under 
    $\tilde{\mathbb P}_\mu := \mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
\[
    \frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}
    \xrightarrow{d} \eta_1, 
    \quad t\rightarrow \infty,
\]
    where $\eta_1$ is a $(1+\beta)$-stable random variable with
\[
    \mathbb{E} [e^{i\theta \eta_1}]
    =\exp(\tilde{m}[\theta f]), 
    \quad \theta\in \mathbb R.
\]
\end{thm}

\subsubsection{Small branching rate}

For $f\in \mathcal{P}$, define
\[
    m[f]
    :=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx
\]
\begin{thm}
\label{Theorem13}
    If $f\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa_f b(1+\beta)$, 
%    then, under 
   then for any $\mu\in \mathcal M_c(\mathbb R_d)$, under 
    $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
    $$\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_2, \quad t\rightarrow \infty,$$
    where $\eta_2$ is a $(1+\beta)$-stable random variable with 
    $$\mathbb{E} [e^{i\theta \eta_2}]=\exp(m[\theta f]), \quad \theta\in \mathbb R.$$
\end{thm}

@@

	For two operators $A: \mathcal D_A \subset \mathcal P^*\to \mathcal P^*$ and $B: \mathcal D_B \subset \mathcal P^*\to \mathcal P^*$, define $(A\times B)f (x):= Af(x) \times Bf(x)$ for all $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb R^d$.
    For any $a > 0$, define $A^{\times a}f(x):= (Af(x))^a$ for all $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
    One of the reason for considering $\gamma$-controllable operators is that they have good algebraic properties:
\begin{lem}
\label{lem: property of controllable operators}
    Let $\mathcal D \subset \mathcal P^*$, $\Lambda$ be an index set, and $(A_\lambda)_{\lambda\in \Lambda}$ be a family of operators from $\mathcal D$ to $ \mathcal P^*$. Assume that $(A_\lambda)_{\lambda\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D$.
\begin{itemize}
\item[(1)]
    Suppose that $(\Lambda, \mathscr F)$ is a measurable space
    and that $(\lambda,x)\mapsto A_\lambda f(x)$ is $\mathscr F \otimes \mathscr B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
    For any probability measure $\nu$ on $(\Lambda, \mathscr F)$, write
\[
    A_\nu f(x):= \int_{\Lambda} A_\lambda f (x)~\nu(d\lambda), \quad f\in \mathcal D, x\in \mathbb R^d.
\]
    Then  $\{A_\nu: \nu \text{ is  a probability measure on } (\Lambda, \mathscr F)\}$ is uniformly $\gamma$-controllable on $\mathcal D$.
\item[(2)]
    Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D_0\subset \mathcal P^*$ to $ \mathcal P^*$.
    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D_0$ for some $\beta \in \mathbb R$ and that, for each $\lambda$, $A_\lambda:\mathcal D \to \mathcal D_0$.
    Then  $(B_\delta A_\lambda)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(\gamma\beta)$-controllable on $\mathcal D$.
\item[(3)]
    Suppose that $\Delta$ is another index set and $(B_\delta)_{\delta\in \Delta}$ is a family of operators from $\mathcal D$ to $ \mathcal P^*$.
    Assume that $(B_\delta)_{\delta\in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D$ for some $\beta \in \mathbb R$.
    Then  $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ is uniformly $(\gamma+\beta)$-controllable.
\item[(4)]
    Let $a>0$. Suppose that, for each $\lambda \in \Lambda$, $A_\lambda : \mathcal D \to \mathcal P^+$.
    Then $(A^{\times a}_\lambda)_{\lambda \in \Lambda}$ is uniformly $(a\gamma)$-controllable.
\end{itemize}
\end{lem}
\begin{proof}
    (1). Let $(R,S)$ be the $\gamma$-control-pair of $(A_\lambda)_{\lambda\in\Lambda}$ on $\mathcal{D}$. For all $f \in \mathcal{D}$, $x\in \mathbb R^d$ and  probability measure $\nu$ on $(\Lambda, \mathscr F)$,
\[
   |A_{\nu}f(x)|\leq \int_{\Lambda}|A_{\lambda}f(x)|\nu(d\lambda) \leq \int_{\Lambda}R|f|(x)\nu(d\lambda) \leq R|f|(x).
\]

@@

\begin{proof}
    (1). It follows from \eqref{eq: upper bound for vf} that for all $g\in \mathcal P$, $0\leq t\leq 1$ and $x\in \mathbb R^d$,
\[
    |U_t g(x)|
    \leq \sup_{0\leq u\leq 1}T_u^\alpha |g| (x).
\]
    Now note that $f\mapsto\sup_{0\leq u\leq 1}T^{\alpha}_u|f|$ is monotone and $1$-scalable.

@@

    (4). From (1), (2), (3) and Lemma \ref{lem: property of controllable operators}.(2), we know that the operators
\[
    f
    \mapsto T^{\alpha}_{t-s}\Psi_0(-U_sf)(x),
    \quad 0\leq s\leq t\leq 1
\]
    are uniformly $(1+\beta)$-controllable.
    Combining this with \eqref{eq:chareq2} and Lemma \ref{lem: property of controllable operators}.(1), we get the desired result.

@@

	In fact, let $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx}.(6).

@@

    According to Corollary \ref{cor: alpha stable rv} and Corollary \ref{cor: used in next corollary}, there exist $C,\delta>0$ such that for any $k\in\{0,1,...,n\}$, we have
